Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-14 manuscript.tex
Figure 1

%----------------------------%
\begin{figure}
\centering
\includegraphics[width=.75\textwidth]{figures/visual-latency.pdf}
% thorpe
% \includegraphics[width=.7\textwidth]{figures/visual-latency-estimate.jpg}%-estimate.jpg}
\caption{{\bf Latency of the different processing steps along the visual pathway.} Though this system is highly inter-connected, one can follow the sequence of activations whenever an image (here a yellow star) is flashed in front of the eyes. Different areas are schematically represented by ellipses and arrows denotes the fastest feed-forward activation, ordered with respect to their activation latency. In order, the retina is first activated ($20-40~\ms$) then the thalamus and the primary visual cortex (V1, $60-80~\ms$). Visual information used for object recognition follows the temporal lobe to reach the infero-temporal area (IT, $100-120~\ms$), and then the prefrontal cortex (PFC) which modulates decision making and the Motor cortex (MC, $140-190~\ms$) which mediates a motor action which is then relayed through the spinal chord to finger muscles, with latencies about $200-350~\ms$.}\label{fig:thorpe}
\end{figure}
%----------------------------%
In particular, there have been some remarkable findings when studying the dynamics of vision. For instance, Simon Thorpe's group has shown during the last decades numerous examples demonstrating that humans can categorize briefly presented images in a fraction of a second. His experiments consisted in asking subjects to categorize images that do or do not contain animals~\citep{thorpe_speed_1996}. The results showed that humans were able to perform this task very well (with a success rate of more than 95\%) but above all that a differential activity for the two categories of images could be observed by electroencephalography, showing that this differentiation emerges with a very short latency in neural activity. These results have been extended to several species, including primates. Different experimental protocols have shown for example that the motor response could be extremely fast (of the order of $120~\ms$) when the task was to perform a saccade~\citep{kirchner_ultra-rapid_2006}. This fast processing correlates with the surprising experiments of fast serial detection, which consists in presenting a fast succession of different images and to decode via the EEG if the observer can detect for example the presence of an animal~\citep{keysers_speed_2001}. As expected, the performances decrease progressively as the frequency of presentation of the images increases. However, it has been shown in the macaque that a significant performance could be maintained with an image presentation time of only $14~\ms$ per image.

>>>>

%----------------------------%
\begin{figure}
\centering
\includegraphics[width=.75\textwidth]{figures/visual-latency.pdf}
% thorpe
% \includegraphics[width=.7\textwidth]{figures/visual-latency-estimate.jpg}%-estimate.jpg}
\caption{{\bf Latency of the different processing steps along the visual pathway.} Though this system is highly inter-connected, one can follow the sequence of activations whenever an image (here a yellow star) is flashed in front of the eyes. Different areas are schematically represented by ellipses and arrows denotes the fastest feed-forward activation, ordered with respect to their activation latency. In order, the retina is first activated ($20-40~\ms$) then the thalamus and the primary visual cortex (V1, $60-80~\ms$). Visual information used for object recognition follows the temporal lobe to reach the infero-temporal area (IT, $120-140~\ms$), and then the prefrontal cortex (PFC) which modulates decision making and the Motor cortex (MC, $140-190~\ms$) which mediates a motor action which is then relayed through the spinal chord to trigger finger muscles, with latencies about $200-350~\ms$.}\label{fig:thorpe}
\end{figure}
%----------------------------%
In particular, there have been some remarkable findings when studying the dynamics of vision. For instance, Simon Thorpe's group has shown during the last decades numerous examples demonstrating that humans can categorize briefly presented images in a fraction of a second. His experiments consisted in asking subjects to categorize images that do or do not contain animals~\citep{thorpe_speed_1996}. The results showed that humans were able to perform this task very well (with a success rate of more than 95\%) but above all that a differential activity for the two categories of images could be observed by electroencephalography, showing that this differentiation emerges with a very short latency in neural activity. These results have been extended to several species, including primates. Different experimental protocols have shown for example that the motor response could be extremely fast (of the order of $120~\ms$) when the task was to perform a saccade~\citep{kirchner_ultra-rapid_2006}. This fast processing correlates with the surprising experiments of fast serial detection, which consists in presenting a fast succession of different images and to decode via the EEG if the observer can detect for example the presence of an animal~\citep{keysers_speed_2001}. As expected, the performances decrease progressively as the frequency of presentation of the images increases. However, it has been shown in the macaque that a significant performance could be maintained with an image presentation time of only $14~\ms$ per image.
